---
output:
  bookdown::pdf_book: # comment when rendering to word document
  # bookdown::word_document2: # uncomment if rendering to word document
    toc: no # change me to yes if rendering to Word
    keep_tex: no
    number_sections: yes
    fig_width: 6
    fig_height: 4
    latex_engine: xelatex
    includes:
        in_header: ./Preamble2.tex
# bibliography: ./References/reference_list.bib
# csl: ./References/reference_format.csl
---


```{r setup, include=FALSE, eval = T}

knitr::opts_chunk$set(echo = FALSE)
options(knitr.duplicate.label = 'allow')


# These libraries are only needed for examples in the introduction 
library("png")
library("grid")
# These are needed in case you are having a glossary
library("knitr")
library("kableExtra")
library("dplyr")
library("tibble")
library("here")


```

<!-- Title page -->

```{r Cover, child = './Sections/00_Cover.Rmd', eval = T}
```

<!-- Set numbers in non Arabic format. And starts in page II as required by G+PS.
NOTE: Remove normal markdown chapters before rendering to PDF  -->
\pagenumbering{roman}
\setcounter{page}{2}

<!-- # Committee form -->

<!-- ```{r Committee_form, child = './Sections/01_Committee_form.Rmd', eval = T} -->
<!-- ``` -->

<!-- \clearpage -->

<!-- Global page configuration -->

\setlength{\parindent}{4em} 
\linespread{1}
\doublespacing

<!-- # Abstract -->

<!-- \section*{Abstract} -->
<!-- \addcontentsline{toc}{section}{Abstract}  -->

<!-- ```{r Abstract, child = './Sections/02_Abstract.Rmd', eval = T} -->
<!-- ``` -->

<!-- \clearpage -->

<!-- # Lay Summary -->

<!-- \section*{Lay Summary} -->
<!-- \addcontentsline{toc}{section}{Lay Summary} -->

<!-- ```{r Lay_abstract, child = './Sections/03_Lay_abstract.Rmd', eval = T} -->
<!-- ``` -->

<!-- \clearpage -->

<!-- # Preface -->

<!-- \section*{Preface} -->
<!-- \addcontentsline{toc}{section}{Preface} -->

<!-- ```{r Preface, child = './Sections/04_Preface.Rmd', eval = T} -->
<!-- ``` -->

<!-- \clearpage -->


<!-- Include a table of contents (including list of figures and tables) without numbering and with dots -->


\addcontentsline{toc}{section}{Table of Contents}

\thispagestyle{empty}
\begin{singlespace}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\setcounter{tocdepth}{3}
\tableofcontents
\clearpage
\addcontentsline{toc}{section}{List of Tables}
\listoftables
\clearpage
\addcontentsline{toc}{section}{List of Figures}
\listoffigures
\clearpage
\end{singlespace}


<!-- # Glossary -->
\section*{Glossary}
\addcontentsline{toc}{section}{Glossary}

```{r Glossary, child = './Sections/05_Glossary.Rmd', eval = T}
```

\clearpage


<!-- # Acknowledgements -->
<!-- \section*{Acknowledgements} -->
<!-- \addcontentsline{toc}{section}{Acknowledgements} -->

<!-- ```{r Acknowledgements, child = './Sections/06_Acknowledgements.Rmd', eval = T} -->
<!-- ``` -->

<!-- \clearpage -->

<!-- Dedication -->
<!-- \section*{Dedication} -->
<!-- \addcontentsline{toc}{section}{Dedication} -->

<!-- ```{r Dedication, child = './Sections/07_Dedication.Rmd', eval = T} -->

<!-- ``` -->


<!-- \clearpage -->

# Introduction

<!-- Set Numbering properly for rest of the document -->
\pagenumbering{arabic}

<!-- This code will needs to be before each chapter so figures and tables numbering are according to each chapter -->
<!-- Note that the chapter number changes each time -->

\renewcommand{\thefigure}{1.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{1.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{1.\arabic{equation}}
\setcounter{equation}{0}

```{r Introduction, child = './Sections/080_Introduction.Rmd', eval = T}
```

## Modelling and Estimation {#SS:intro-modelling}

```{r Introduction2, child = './Sections/081_IntroModelling.Rmd', eval = T}
```

\clearpage

<!-- From here on, include your different data chapters using normal Rmarkdown titles -->

<!-- Modify me! -->
# Background on Densities with Homothetic Level Sets {#S:background}

<!-- Set figure and table numbering according to the chapter -->
\renewcommand{\thefigure}{2.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{2.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{2.\arabic{equation}}
\setcounter{equation}{0}

```{r Background, child = './Sections/0900_Background.Rmd', eval = T}
```

## Definitions {#definitions}

```{r Background1, child = './Sections/0910_Definitions.Rmd', eval = T}
```

## Density Generator {#density-generator}

```{r Background2, child = './Sections/0920_DensityGenerator.Rmd', eval = T}
```

## Simulation of Random Vectors with Density $f \in \HC{D}$ {#stochastic-representation}

```{r Background3, child = './Sections/0930_Simulation.Rmd', eval = T}
```

### Simulation over Boundary of Shape Set {#sim-boundary}

```{r Background32, child = './Sections/0931_Boundary.Rmd', eval = T}
```

### Simulation over Shape Set {#sim-shapeset}

```{r Background33, child = './Sections/0932_ShapeSet.Rmd', eval = T}
```

\clearpage

<!-- Modify me! -->
# Estimation of Homothetic Densities {#estimation}

<!-- Set figure and table numbering according to the chapter -->
\renewcommand{\thefigure}{3.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{3.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{3.\arabic{equation}}
\setcounter{equation}{0}

```{r ShapeSet, child = './Sections/1000_Estimation.Rmd', eval = T}
```

## Shape Set Estimation {#S:shape-set}

```{r ShapeSet1, child = './Sections/1010_ShapeSet.Rmd', eval = T}
```

### Kernel Density Estimation {#SSS:kde}

```{r ShapeSet2, child = './Sections/1011_KernelDensity.Rmd', eval = T}
```

### Conditional Mean of the Radial Variable {#SSS:regression}

```{r ShapeSet2, child = './Sections/1012_ConditionalMean.Rmd', eval = T}
```

<!-- #### Kernel Regression -->

<!-- ```{r ShapeSet3, child = './Sections/1012_KernelRegression.Rmd', eval = T} -->
<!-- ``` -->

<!-- #### Smoothing Splines -->

<!-- ```{r ShapeSet4, child = './Sections/1013_SmoothingSplines.Rmd', eval = T} -->
<!-- ``` -->

#### Free-Knot Splines {#SSS:free-knot-splines}

```{r ShapeSet5, child = './Sections/1014_FreeKnotSplines.Rmd', eval = T}
```

## Density Estimation {#S:estimation-dg}

```{r ShapeSet6, child = './Sections/1030_DensityEstimation.Rmd', eval = T}
```

\clearpage

<!-- Modify me! -->
# Trochoidal Distributions {#SS:trochoidal-dist}

<!-- Set figure and table numbering according to the chapter -->
\renewcommand{\thefigure}{4.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{4.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{4.\arabic{equation}}
\setcounter{equation}{0}

```{r Trochoidal, child = './Sections/1100_TrochoidalDist.Rmd', eval = T}
```

## Bivariate Normal Example {#SS:biv-norm-example}

```{r Trochoidal2, child = './Sections/1110_BivNorm.Rmd', eval = T}
```

## Trochoidal Distribution Example

```{r Trochoidal3, child = './Sections/1120_Trochoid.Rmd', eval = T}
```

\clearpage

<!-- Modify me! -->
# Remaining Research Objectives {#S:objectives}

<!-- Set figure and table numbering according to the chapter -->
\renewcommand{\thefigure}{5.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{5.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{5.\arabic{equation}}
\setcounter{equation}{0}

```{r Objectives, child = './Sections/1200_Objectives.Rmd', eval = T}
```

\clearpage

<!-- # References -->
\section*{References}
\addcontentsline{toc}{section}{References}

<!-- Reset page config. For proper referencing  -->
\noindent
\leftskip=2em
\parindent=-2em
\begin{singlespace}
\bibliographystyle{chicago} 
\bibliography{`r as.name(here::here("References", "reference_list.bib"))`}

\end{singlespace}
<div id="refs"></div>

\clearpage

<!-- Go back to original page config. -->
\setlength{\parindent}{4em} 
\linespread{1}
\doublespacing


<!-- # Appendices -->
<!-- \section*{Appendices} -->
<!-- \addcontentsline{toc}{section}{Appendices} -->

<!-- ## Appendix A {#S:App-splines} -->

<!-- \section*{Appendix A - Supplementary Information for Smoothing Cubic Splines} -->
<!-- \addcontentsline{toc}{section}{Appendix A} -->

<!-- <!-- Set Figure, table and equations numbering according to the chapter -->
<!-- \renewcommand{\thefigure}{A2.\arabic{figure}} -->
<!-- \setcounter{figure}{0} -->
<!-- \renewcommand{\thetable}{A2.\arabic{table}} -->
<!-- \setcounter{table}{0} -->
<!-- \renewcommand{\theequation}{A2.\arabic{equation}} -->
<!-- \setcounter{equation}{0} -->


<!-- ```{r AppendixA, child = './Sections/9999_Appendix-Splines.Rmd', eval = T} -->
<!-- ``` -->


<!-- ## Appendix B  -->

<!-- \section*{Appendix B - Supplementary information for "Name of Chapter Three"} -->
<!-- \addcontentsline{toc}{section}{Appendix B} -->

<!-- Set Figure, table and equations numbering according to the chapter -->
<!-- \renewcommand{\thefigure}{A3.\arabic{figure}} -->
<!-- \setcounter{figure}{0} -->
<!-- \renewcommand{\thetable}{A3.\arabic{table}} -->
<!-- \setcounter{table}{0} -->
<!-- \renewcommand{\theequation}{A3.\arabic{equation}} -->
<!-- \setcounter{equation}{0} -->


<!-- ```{r appendix_b, child = '~/GitHub/TransEmergence/Scripts/Supplements.Rmd', eval = F} -->
<!-- ``` -->

<!-- END OF SCRIPT -->
