

In this section, we develop an iterative approach for estimating a \ac{pdf} $f \in \HC{D}$ on $\R^2$ from data $\xb_1, \dots, \xb_n$ by combining shape set estimators in Equations \eqref{Eq:estimator-Kamiya} and \eqref{Eq:free-knot-estimator} with \ac{ml} estimation for the density generator. Given known location parameter $\mub = \zerob$, the iterative approach is as follows:

  - Use Kamiya's estimator in Equation \eqref{Eq:K-standard} to produce a first estimate of the shape set, $\est{D}^{(1)}$, and its corresponding gauge function, $\fncD[\est{D}^{(1)}]{n}{\xb}$.
  - Estimate the star-generalized radii to produce the psuedo-sample, \eqq{
  \est{r}_i^{(1)} = \fncD[\est{D}^{(1)}]{n}{\xb_i}, \qquad i = 1, \dots, n.
  }
  - By assuming a Weibull-type density generator \eqq{
    \fnc{f_0}{r} \ \propto \ \expo{-\paren{\frac{r}{\s}}^{\xi}}, \qquad r > 0,
    } with scale parameter $\s > 0$ and shape parameter $\xi > 0$, we are assuming the data follow a distribution with density \eqq{
    \fnc{f}{\xb} = \fnc{f_0}{\fncD{n}{\xb}} = \frac{1}{\abs{D}\s^2\fnc{\Gamma}{\frac{2+\xi}{\xi}}}\expo{-\paren{\frac{\fncD{n}{\xb}}{\s}}^{\xi}}, \qquad \xb \in \R^2.
    } The density for the star-generalized radius variable follows from Equation \eqref{Eq:scale-r}, \eqq{
    \fnc{f_R}{r} = \frac{2}{\s^2\fnc{\Gamma}{\frac{2+\xi}{\xi}}}r\expo{-\paren{\frac{r}{\s}}^{\xi}}, \qquad r > 0.
    } Estimate the parameters of $f_0$ using \ac{ml} by maximizing the log-likelihood function, \eqq{
    \fnc{\ell}{\s, \xi; \est{r}_1^{(1)}, \dots, \est{r}_n^{(1)}} = n\fnc{\log}{2} - 2n\fnc{\log}{\s} - n\fnc{\log}{\fnc{\Gamma}{\frac{2+\xi}{\xi}}} + \sumto{i=1}{n}\fnc{\log}{\est{r}_i^{(1)}} - \sumto{i=1}{n}\paren{\frac{\est{r}_i^{(1)}}{\s}}^{\xi}.
  }
  - Use the \ac{ml} estimates $\paren{\est{\s}^{(1)}, \est{\xi}^{(1)}}$ to specify the density generator and the free-knot spline estimator in Equation \eqref{Eq:free-knot-estimator} to produce $\est{D}^{(2)}$ and its corresponding gauge function, $\fncD[\est{D}^{(2)}]{n}{\xb}$.
  - Update the estimates of the star-generalized radii to produce the psuedo-sample, \eqq{
  \est{r}_i^{(2)} = \fncD[\est{D}^{(2)}]{n}{\xb_i}, \qquad i = 1, \dots, n.
  }
  - Update the density generator parameter estimates to $\paren{\est{\s}^{(2)}, \est{\xi}^{(2)}}$ by maximizing the log-likelihood function, \eqq{
    \fnc{\ell}{\s, \xi; \est{r}_1^{(2)}, \dots, \est{r}_n^{(2)}} = n\fnc{\log}{2} - 2n\fnc{\log}{\s} - n\fnc{\log}{\fnc{\Gamma}{\frac{2+\xi}{\xi}}} + \sumto{i=1}{n}\fnc{\log}{\est{r}_i^{(2)}} - \sumto{i=1}{n}\paren{\frac{\est{r}_i^{(2)}}{\s}}^{\xi}.
  }
  
<!-- In the next section, we apply the iterative method as outlined above to estimate the densities for the simulated datasets outlined in Section \@ref(S:shape-set). While we do not go beyond the above steps, it should noted that the iterative method can be extended. The parameter estimates for the density generator can be updated using the data, $\est{r}_i^{(2)} = \fncD[\est{D}^{(2)}]{n}{\xb}$. Then, the updated density generator can be plugged back into the free-knot spline estimator to update the shape set estimate. This process can be repeated until convergence.  -->

<!-- Regardless of the approach to estimating the density generator, we employ the iterative approach of Section \@ref(estimation). In particular, we use Kamiya's estimator in Equation \eqref{Eq:K-standard} to estimate the gauge function for $D$ as $\fncD[\est{D}^{(1)}]{n}{\xb}$, assuming $\mub = \zerob$. We then calculate the estimates of the star-generalized radii for each observation as $\fncD[\est{D}^{(1)}]{n}{\xb} = r_i^{(1)}$. Further assuming a parametric form for the density generator, we use \ac{ml} estimation and denote the estimate of the density generator as $\est{f}_0^{(1)}$. -->

<!-- We can now use $\est{f}_0^{(1)}$ to re-estimate the shape set. For example, we can specify the density generator as $\est{f}_0^{(1)}$ and adopt the free-knot spline estimator in Equation \eqref{Eq:free-knot-estimator}. Or we can use a nonparametric method such as kernel regression and choose the bandwidth argument by maximizing the likelihood assuming $f_0 = \est{f}_0^{(1)}$. This produces another estimate for the gauge function, $\fncD[\est{D}^{(2)}]{n}{\xb}$, which can be used to update our estimates of the star-generalized radii, $\fncD[\est{D}^{(2)}]{n}{\xb} = r_i^{(2)}$, which in turn can be used to update our estimate of $f_0$ to $\est{f}_0^{(2)}$. This process is referred to as the iterative method and is similar to the EM-Algorithm \citep{Dempster1977}. -->

<!-- ### Shape Set and Scaling {#SSS:shape-set-scaling} -->

<!-- To facilitate estimation of $f\in\HC{D}$ that is computationally efficient and parsimonious, we take a closer look at the gauge function in defining the shape set. From Equation \eqref{Eq:D-boundary}, there is a clear relationship between $\fnc{n_D}{\xb - \mub}$ for points $\xb \in \pd D$ and the polar function $\fncD{r}{\tbm}$. In Section \@ref(S:shape-set), we have seen that approaches to estimating $\fncD{r}{\t}$ are readily available, well-established, and provide a general approach for estimation of $D$ up to proportion. The unresolved issue thus far is the potential effect of the proportion $\ka > 0$. We now show that for the normal distribution we can either incorporate a scaling parameter into the density generator or scale the shape set using the homogeneity property of the gauge function. -->

<!-- Assume we have the random vector \eqq{ -->
<!--   \Xb = \bmat{X_1 \\ X_2} \sim \dist{N}{\bmat{0 \\ 0}, \bmat{1 & 0 \\ 0 & 1}}. -->
<!-- } The density generator takes the form \eqq{ -->
<!--   \fnc{f_0}{\fnc{n_D}{\xb}} \ \propto \ e^{-\fnc{n_D}{\xb}^2/2}, -->
<!-- } with normalizing constant $p\abs{D} = 2\pi$ using Equation \eqref{Eq:normalizing-constant}. -->

<!-- Now suppose we scaled the components of $\Xb$ equally by $\s$. Let $\Yb = \s\Xb$. Then, \eqq{ -->
<!--   \Yb = \bmat{Y_1 \\ Y_2} \sim \dist{N}{\bmat{0 \\ 0}, \bmat{\s^2 & 0 \\ 0 & \s^2}}. -->
<!-- } We have a choice of placing a scaling parameter into the density generator, \eqq{ -->
<!--   \fnc{f_{01}}{\fnc{n_D}{\xb}} \ \propto \ \expo{-\frac{\fnc{n_D}{\xb}^2}{2\s^2}}, -->
<!-- } or into the shape set $E = \s D$. -->

<!-- Let's look at each situation in turn. If we incorporate the scaling parameter into the density generator, then our shape set remains as the circle $D$ with radius $1$. The terms of the normalizing constant that lie outside the integral in Equation \eqref{Eq:normalizing-constant} are unchanged, $p\abs{D} = 2\pi$. However, the integral portion produces \eqq{ -->
<!--   \int_{0}^{\nf}r\expo{-\frac{r^2}{2\s^2}}dr = \s^2, -->
<!-- } and we get the familiar normalizing constant $2\s^2\pi$ for a bivariate isotropic normal density. -->

<!-- This result continues to hold for the bivariate normal family. Consider the anisotropic normal density with covariance matrix $\Sigma \in \R^{2\times2}$ with components $\s_{ij}$. The positive-definiteness of $\Sigma$ guarantees its diagonalization and thus there are two eigenvalues $\l_1$ and $\l_2$ which represent a stretching of the circle of radius $1$ in orthogonal directions of their corresponding eigenvectors. Standardizing the eigenvalues to $\l_1 = 1$ and $\l_2 = \l_2/\l_1$, we can write the covariance matrix as \eqq{ -->
<!--   \Sigma = V\tr DV = \l_1 V\tr \bmat{1 & 0 \\ 0 & \l_2/\l_1} V = \l_1\widetilde{\Sigma}, -->
<!-- } and we again have the option of accounting for the scaling in the shape set or the density generator. In the former case, we need not worry about the value of $\l_1$ explicitly and the resulting star-generalized radius variables are standardized to have scale 1. For the bivariate normal distribution, the shape set could then be viewed as \eqq{ -->
<!--   \fnc{\de}{\xb; \mub, \Sigma} = \paren{\xb - \mub}\tr\Sigma^{-1}\paren{\xb - \mub} = \frac{1}{\l_1}\paren{\xb - \mub}\tr\widetilde{\Sigma}^{-1}\paren{\xb - \mub} = \zb\tr\widetilde{\Sigma}^{-1}\zb, -->
<!-- } for standard bivariate normal vector $\zb$. -->

<!-- A goal of this research is to confirm that this conclusion holds in general for densities $f\in\HC{D}$. In particular, show that estimation is unaffected by whether a scaling parameter is included in the density generator or the shape set, and be sure that the identifiability property for distributions is not violated \citep[p. 11]{Liebscher2016}. -->

```{r dg-estimate-one, echo=FALSE}
## Load Simulated data
sim.1 <- readRDS(gsub("ubcdown", "", here::here("Thesis", "data", "sim.1.norm.RDS")))
# sim.2 <- readRDS(here::here("Thesis", "data", "sim.2.log.RDS"))

## Load data for Kamiya's estimate
kde.1 <- readRDS(gsub("ubcdown", "", here::here("Thesis", "data", "kde.1.norm.RDS")))
# kde.2 <- readRDS(here::here("Thesis", "data", "kde.2.log.RDS"))

## Extract star-generalized radius variables
rho.1 <- sim.1$r
rho.1.kde <- sqrt(kde.1$df.obs$Dhat.x1^2 + kde.1$df.obs$Dhat.x2^2)
rstar.1 <- rho.1/rho.1.kde

# rho.2 <- sim.2$r
# rho.2.kde <- sqrt(kde.2$df.obs$Dhat.x1^2 + kde.2$df.obs$Dhat.x2^2)
# rstar.2 <- rho.2/rho.2.kde

## Starting Values for MLE
fnd.shape <- function(c, sigma, mu) { 
  (sigma/mu)^2 - (gamma(1 + 2/c) - gamma(1 + 1/c)^2)/gamma(1 + 1/c)^2
}

## Simulation 1 starting values
xi.tmp <- uniroot(fnd.shape, interval=c(0.1, 3), sigma=sd(rstar.1), mu=mean(rstar.1))$root
strt.1 <- list('scale'=(mean(rstar.1)/gamma(1 + 1/xi.tmp))^xi.tmp, 'shape'=xi.tmp)
rm(xi.tmp)

## Simulation 2 starting values
# xi.tmp <- uniroot(fnd.shape, interval=c(0.1, 3), sigma=sd(rstar.2), mu=mean(rstar.2))$root
# strt.2 <- list('scale'=(mean(rstar.2)/gamma(1 + 1/xi.tmp))^xi.tmp, 'shape'=xi.tmp)
# rm(xi.tmp)

## Weibull MLE
nllk.wbl.r <- function(pms, r) {
  sigma <- pms[1]; xi <- pms[2]
  
  if (sigma <= 1e-4 | xi <= 1e-4) {
    ans <- 1e8
  } else {
    n <- length(r)
    t.1 <- n*log(2)
    t.2 <- 2*n*log(sigma)
    t.3 <- n*lgamma((2+xi)/xi)
    t.4 <- sum(log(r))
    t.5 <- sum((r/sigma)^xi)
    
    llik <- t.1 - t.2 - t.3 + t.4 - t.5
    ans <- -llik
  }
  return(ans)
}

fullmle.1 <- nlm(nllk.wbl.r, p=c(strt.1$scale, strt.1$shape), r=rstar.1, hessian=TRUE)
if (all(abs(fullmle.1$gradient) < 1e-2)) {
  mle.1 <- list('scale'=fullmle.1$estimate[1], 'shape'=fullmle.1$estimate[2])
} else {
  mle.1 <- strt.1
}
se.1 <- list('scale.se'=sqrt(diag(solve(fullmle.1$hessian))[1]), 
             'shape.se'=sqrt(diag(solve(fullmle.1$hessian))[2]))

## Free-Knot Spline estimate
fks.1 <- readRDS(gsub("ubcdown", "", here::here("Thesis", "data", "rjmcmc.sim1.wbl.RDS")))
## Re-estimate star-generalized radii
rstar.1v2 <- (fks.1$r.obs/fks.1$Dhat.obs)
## Re-run ML with Weibull-type Generator using updated star-generalized radii
xi.tmp <- uniroot(fnd.shape, interval=c(0.1, 3), sigma=sd(rstar.1v2), mu=mean(rstar.1v2))$root
strt.1 <- list('scale'=(mean(rstar.1v2)/gamma(1 + 1/xi.tmp))^xi.tmp, 'shape'=xi.tmp)
rm(xi.tmp)
fullmle.1v2 <- nlm(nllk.wbl.r, p=c(strt.1$scale, strt.1$shape), r=rstar.1v2, hessian=TRUE)
if (all(abs(fullmle.1v2$gradient) < 1e-2)) {
  mle.1v2 <- list('scale'=fullmle.1v2$estimate[1], 'shape'=fullmle.1v2$estimate[2])
} else {
  mle.1v2 <- strt.1
}
se.1v2 <- list('scale.se'=sqrt(diag(solve(fullmle.1v2$hessian))[1]), 
             'shape.se'=sqrt(diag(solve(fullmle.1v2$hessian))[2]))

# fullmle.2 <- nlm(nllk.wbl.r, p=c(strt.2$scale, strt.2$shape), r=rstar.2)
# if (all(abs(fullmle.2$gradient) < 1e-2)) {
#   mle.2 <- list('scale'=fullmle.2$estimate[1], 'shape'=fullmle.2$estimate[2])
# } else {
#   mle.2 <- strt.2
# }
```

Using the simulated dataset from Section \@ref(S:shape-set) with density given by Equation \eqref{Eq:Simulation-1}, we apply the iterative method outlined above to estimate $f$. Assuming a Weibull-type density generator, the true parameters are $\s_0 = \sqrt{2}$ and $\xi_0 = 2$. Results for each step are given in Figure \ref{Fig:iterative-1}. Plot (a) shows the shape set \mbox{estimate $\est{D}^{(1)}$} against the true shape set. Plot (b) presents a QQ-plot of the star-generalized radius variables for the estimated Weibull-type density generator with estimated scale \mbox{parameter, $\est{\s}^{(1)} = `r round(mle.1$scale, 2)`$}, with standard \mbox{error $\fnc{\text{SE}}{\est{\s}^{(1)}} = `r round(se.1$scale.se, 2)`$} and estimated shape \mbox{parameter, $\est{\xi}^{(1)} = `r round(mle.1$shape, 2)`$}, with standard \mbox{error $\fnc{\text{SE}}{\est{\xi}^{(1)}} = `r round(se.1$shape.se, 2)`$} against the true star-generalized radii. Plot (c) presents the updated shape set \mbox{estimate $\est{D}^{(2)}$} from the free-knot spline estimator. Plot (d) is analogous to Plot (b), but uses the estimated scale \mbox{parameter, $\est{\s}^{(2)} = `r round(mle.1v2$scale, 2)`$}, with standard \mbox{error $\fnc{\text{SE}}{\est{\s}^{(1)}} = `r round(se.1v2$scale.se, 2)`$} and estimated shape \mbox{parameter, $\est{\xi}^{(2)} = `r round(mle.1v2$shape, 2)`$}, with standard \mbox{error $\fnc{\text{SE}}{\est{\xi}^{(1)}} = `r round(se.1v2$shape.se, 2)`$}. These preliminary results are promising in that the shape set estimates and the density generator parameter estimates better fit the data in the subsequent iteration.

```{r plots-sim-1, fig.height=7, fig.width=8, fig.cap="\\label{Fig:iterative-1}Iterative approach to estimating the density in Equation \\ref{Eq:Simulation-1} from data simulated from the density: Plot (a) presents the shape set estimate $\\est{D}^{(1)}$; Plot (b) presents a QQ-plot of the estimated star-generalized radius density with parameter estimates $\\paren{\\est{\\s}^{(1)}, \\est{\\xi}^{(1)}}$; Plot (c) presents the shape set estimate $\\est{D}^{(2)}$; Plot (d) presents the QQ-plot of the estimated star-generalized radius density with parameter estimates $\\paren{\\est{\\s}^{(2)}, \\est{\\xi}^{(2)}}$.", cache=TRUE, echo=FALSE}
bdry.1 <- readRDS(gsub("ubcdown", "", here::here("Thesis", "data", "bdry.1.norm.RDS")))
par(mfrow=c(2,2))
## Kamiya's Shape Set Estimate
plot(bdry.1$x1, bdry.1$x2, type='l', main="Kamiya's Shape Set", sub="(a)",
     xlim=c(-1.1, 1.1), ylim=c(-1.1, 1.1), xlab=expression(x[1]), ylab=expression(x[2]),
     lty=1, col=scales::alpha("black", 0.75))
lines(kde.1$df.grid$Dhat.x1, kde.1$df.grid$Dhat.x2, lty=2,
      col="red")
legend('topright', legend=c("True", "Estimate"), bty="n", cex=0.75,
       lty=c(1, 2), col=c(scales::alpha("black", 0.75), "red"))

## 1st QQ-Plot of Star-generalized radius - Kamiya ML Estimate vs. True
pwbl.r <- function(r, sigma, xi) {
  ans <- numeric(length=length(r))
  for (i in seq_along(r)) {
    t.1 <- 2*r^2
    t.2 <- integrate(f=function(t, n, z){ exp(-z*t)/t^n }, lower=1, upper=Inf, n=1-2/xi, z=(r/sigma)^xi)$value
    t.3 <- xi*sigma^2*gamma(2/xi + 1)
    ans[i] <- 1 - t.1*t.2/t.3
  }
  return(ans)
}
qwbl.r <- function(p, sigma, xi) {
  q.fnc <- function(r, sigma, xi, p) {
    p - pwbl.r(r=r, sigma=sigma, xi=xi)
  }
  q <- numeric(length=length(p))
  for (i in seq_along(p)) {
    p.tmp <- p[i]
    q[i] <- uniroot(f=q.fnc, interval=c(1e-2, 10), sigma=sigma, xi=xi, p=p.tmp)$root
    rm(p.tmp)
  }
  return(q)
}
p <- seq_along(rstar.1)/(length(rstar.1) + 1)
# the.q <- qwbl.r(p=p, sigma=mle.1$scale, xi=mle.1$shape)
# emp.q <- sort(rstar.1)
est.q <- qwbl.r(p=p, sigma=mle.1$scale, xi=mle.1$shape)
true.q <- sort(sim.1$stargen)
p.lims <- c(0, max(est.q, true.q))
plot(est.q, true.q, xlab="Weibull Model", ylab="True",
     main="QQ-Plot for Radius", sub="(b)", cex=0.6,
     col=scales::alpha("darkgrey", 0.75), xlim=p.lims, ylim=p.lims)
abline(a=0, b=1)
legend('topleft', legend=c(paste0('scale = ', round(mle.1$scale, 2)), paste0('shape = ', round(mle.1$shape, 2))),
       bty="n", horiz=TRUE, cex=0.75)

## Free-Knot Spline using Weibull MLE
plot(bdry.1$x1, bdry.1$x2, type='l', main="Free-Knot Spline Estimate", sub="(c)",
     xlim=c(-1.1, 1.1), ylim=c(-1.1, 1.1), xlab=expression(x[1]), ylab=expression(x[2]),
     lty=1, col=scales::alpha("black", 0.75))
lines(fks.1$Dhat.grid*cos(fks.1$theta.grid), fks.1$Dhat.grid*sin(fks.1$theta.grid), lty=2,
      col="red")
legend('topright', legend=c("True", "Estimate"), bty="n", cex=0.75,
       lty=c(1, 2), col=c(scales::alpha("black", 0.75), "red"))

## 2nd QQ-Plot of Star-Generalized Radius - Free-Knot Spline ML Estimate vs. True
p <- seq_along(rstar.1v2)/(length(rstar.1v2) + 1)
est.q <- qwbl.r(p=p, sigma=mle.1v2$scale, xi=mle.1v2$shape)
true.q <- sort(sim.1$stargen)
p.lims <- c(0, max(est.q, true.q))
plot(est.q, true.q, xlab="Weibull Model", ylab="True",
     main="QQ-Plot for Radius", sub="(d)", cex=0.6,
     col=scales::alpha("darkgrey", 0.75), xlim=p.lims, ylim=p.lims)
abline(a=0, b=1)
legend('topleft', legend=c(paste0('scale = ', round(mle.1v2$scale, 2)), paste0('shape = ', round(mle.1v2$shape, 2))),
       bty="n", horiz=TRUE, cex=0.75)
## True CDF
# ptrue1.r <- function(r) {
#   1 - exp(-r^2/2)
# }
## True Quantile Function
# qtrue1.r <- function(p) {
#   sqrt(-2*log(1-p))
# }
## Probability Levels from Data
# p <- seq_along(rstar.1)/(length(rstar.1) + 1)
# the.q <- sort(fks.1$r.obs/fks.1$Dhat.obs)
# emp.q <- sort(sim.1$stargen)
# plot(the.q, emp.q, xlab="Weibull Model", ylab="True",
#      main="QQ-Plot for Radius", cex=0.6, xlim=c(0, max(the.q, emp.q)), ylim=c(0, max(the.q, emp.q)),
#      col=scales::alpha("darkgrey", 0.75))
# abline(a=0, b=1)
```

<!-- ### Simulation Example 2 -->

<!-- ```{r plots-sim-2, fig.height=7, fig.width=8, fig.cap="\\label{Fig:diag-sim-1}Comparing estimates to true values for Simulation 2", cache=TRUE} -->
<!-- bdry.2 <- readRDS(here::here("Thesis", "data", "bdry.2.log.RDS")) -->
<!-- par(mfrow=c(2,2)) -->
<!-- ## Kamiya's Shape Set Estimate -->
<!-- plot(bdry.2$x1, bdry.2$x2, type='l', main="Kamiya's Shape Set", -->
<!--      xlim=c(-1.1, 1.1), ylim=c(-1.1, 1.1), xlab=expression(x[1]), ylab=expression(x[2]), -->
<!--      lty=1, col=scales::alpha("black", 0.75)) -->
<!-- lines(kde.2$df.grid$Dhat.x1, kde.2$df.grid$Dhat.x2, lty=2, -->
<!--       col="red") -->
<!-- legend('topright', legend=c("True", "Estimate"), bty="n", cex=0.75, -->
<!--        lty=c(1, 2), col=c(scales::alpha("black", 0.75), "red")) -->

<!-- ## QQ-Plot of R - MLE -->
<!-- pwbl.r <- function(r, sigma, xi) { -->
<!--   ans <- numeric(length=length(r)) -->
<!--   for (i in seq_along(r)) { -->
<!--     t.1 <- 2*r^2 -->
<!--     t.2 <- integrate(f=function(t, n, z){ exp(-z*t)/t^n }, lower=1, upper=Inf, n=1-2/xi, z=(r/sigma)^xi)$value -->
<!--     t.3 <- xi*sigma^2*gamma(2/xi + 1) -->
<!--     ans[i] <- 1 - t.1*t.2/t.3 -->
<!--   } -->
<!--   return(ans) -->
<!-- } -->
<!-- qwbl.r <- function(p, sigma, xi) { -->
<!--   q.fnc <- function(r, sigma, xi, p) { -->
<!--     p - pwbl.r(r=r, sigma=sigma, xi=xi) -->
<!--   } -->
<!--   q <- numeric(length=length(p)) -->
<!--   for (i in seq_along(p)) { -->
<!--     p.tmp <- p[i] -->
<!--     q[i] <- uniroot(f=q.fnc, interval=c(1e-2, 10), sigma=sigma, xi=xi, p=p.tmp)$root -->
<!--     rm(p.tmp) -->
<!--   } -->
<!--   return(q) -->
<!-- } -->
<!-- p <- seq_along(rstar.2)/(length(rstar.2) + 1) -->
<!-- the.q <- qwbl.r(p=p, sigma=mle.2$scale, xi=mle.2$shape) -->
<!-- emp.q <- sort(rstar.2) -->
<!-- plot(the.q, emp.q, xlab="Weibull Model", ylab="Empirical", -->
<!--      main="QQ-Plot for Radius", cex=0.6, -->
<!--      col=scales::alpha("darkgrey", 0.75)) -->
<!-- abline(a=0, b=1) -->

<!-- ## Free-Knot Spline using Weibull MLE -->
<!-- fks.2 <- readRDS(here::here("Thesis", "data", "rjmcmc.sim2.wbl.RDS")) -->
<!-- plot(bdry.2$x1, bdry.2$x2, type='l', main="Free-Knot Spline Estimate", -->
<!--      xlim=c(-1.1, 1.1), ylim=c(-1.1, 1.1), xlab=expression(x[1]), ylab=expression(x[2]), -->
<!--      lty=1, col=scales::alpha("black", 0.75)) -->
<!-- lines(fks.2$Dhat.grid*cos(fks.2$theta.grid), fks.2$Dhat.grid*sin(fks.2$theta.grid), lty=2, -->
<!--       col="red") -->
<!-- legend('topright', legend=c("True", "Estimate"), bty="n", cex=0.75, -->
<!--        lty=c(1, 2), col=c(scales::alpha("black", 0.75), "red")) -->

<!-- ## QQ-Plot of R - True Model -->
<!-- # ptrue1.r <- function(r) { -->
<!-- #   1 - exp(-r^2/2) -->
<!-- # } -->
<!-- # qtrue1.r <- function(p) { -->
<!-- #   sqrt(-2*log(1-p)) -->
<!-- # } -->
<!-- # p <- seq_along(rstar.1)/(length(rstar.1) + 1) -->
<!-- the.q <- sort(fks.2$r.obs/fks.2$Dhat.obs) -->
<!-- emp.q <- sort(sim.2$stargen) -->
<!-- plot(the.q, emp.q, xlab="Weibull Model", ylab="True", -->
<!--      main="QQ-Plot for Radius", cex=0.6, xlim=c(0, max(the.q, emp.q)), ylim=c(0, max(the.q, emp.q)), -->
<!--      col=scales::alpha("darkgrey", 0.75)) -->
<!-- abline(a=0, b=1) -->
<!-- ``` -->


<!-- ### Simultaneous Approach -->

<!-- We use \ac{ml} estimation to estimate both the shape set and the density generator simultaneously. For now, we assume a trochoidal distribution family which implies the boundary of the density level sets are trochoids, and we are free to assume any parametric form for the density generator. The benefit of \ac{ml} estimation is that under an appropriate parametric model and regularity conditions, inference follows from the asymptotically normal distribution of the \ac{ml} estimators. -->

<!-- ### Estimation of the Density Generator {#SSS:estimation-dg} -->

<!-- Research needs to be performed. Preliminary ideas discussed in Section \@ref(SSS:estimation-of-dg). -->

<!-- ### Assessing Estimation {#SSS:estimation-assessment} -->

<!-- Research needs to be performed. Preliminary ideas discussed in Section \@ref(S:objectives). -->


